\begin{itemize}
        \item G.-S. Xia, J. Hu, F. Hu, B. Shi, X. Bai, Y. Zhong, L. Zhang, and X. Lu, ``AID: A benchmark data set for performance evaluation of aerial scene classification,'' *IEEE Trans. Geosci. Remote Sens.*, vol. 55, no. 7, pp. 3965--3981, Jul. 2017.

    \item G. Cheng, J. Han and X. Lu, "Remote Sensing Image Scene Classification: Benchmark and State of the Art," in Proceedings of the IEEE, vol. 105, no. 10, pp. 1865-1883, Oct. 2017, doi: 10.1109/JPROC.2017.2675998.

    \item Y. Yang and S. Newsam, “Geographic image retrieval using local invariant features,” IEEE Trans. Geosci. Remote Sens., vol. 51, no. 2, pp. 818–832, Feb. 2013.

    \item Braj Raj Nagar, "optimal-31", avilable in: www.kaggle.com/datasets/brajrajnagar/optimal-31, access on 24-06-2025

    \item Yang, Y.; Newsam, S. Bag-of-visual-words and spatial extensions for land-use classification. In Proceedings of the 18th SIGSPATIAL International Conference on Advances in Geographic Information Systems—GIS ’10, San Jose, CA, USA, 2–5 November 2010; p. 270.

    \item P. Deng, K. Xu and H. Huang, "When CNNs Meet Vision Transformer: A Joint Framework for Remote Sensing Scene Classification," in IEEE Geoscience and Remote Sensing Letters, vol. 19, pp. 1-5, 2022, Art no. 8020305, doi: 10.1109/LGRS.2021.3109061.

    \item T. Peng, J. Yi and Y. Fang, "A Local–Global Interactive Vision Transformer for Aerial Scene Classification," in IEEE Geoscience and Remote Sensing Letters, vol. 20, pp. 1-5, 2023, Art no. 6004405, doi: 10.1109/LGRS.2023.3266008.
    
    \item Bazi Y, Bashmal L, Rahhal MMA, Dayil RA, Ajlan NA. Vision Transformers for Remote Sensing Image Classification. Remote Sensing. 2021; 13(3):516. https://doi.org/10.3390/rs13030516 
    
    \item Luo J, Wang Y, Ou Y, He B, Li B. Neighbor-Based Label Distribution Learning to Model Label Ambiguity for Aerial Scene Classification. Remote Sensing. 2021; 13(4):755. https://doi.org/10.3390/rs13040755 

    \item M. A. Arefeen, S. T. Nimi, M. Y. S. Uddin and Z. Li, "A Lightweight Relu-Based Feature Fusion For Aerial Scene Classification," 2021 IEEE International Conference on Image Processing (ICIP), Anchorage, AK, USA, 2021, pp. 3857-3861, doi: 10.1109/ICIP42928.2021.9506524.

    \item A. Alencar, R. Silvestrini, J. Gomes and G. Savian, “Amazônia em Chamas: O Novo e Alarmante Patamar do Desmatamento na Amazônia,”  Instituto de Pesquisa Ambiental da Amazônia (IPAM), Nota Técnica nº 9, fev. 2022.

    \item E. Bastos Furtado, T. Franchi, L. Barreto Rodrigues and G. Da Frota Simões, “Asas que Devastam a Amazônia: Uma Análise do Cenário de Pistas de Pouso e Voos Irregulares que Dão Suporte ao Garimpo Ilegal na TI Yanomami,”  Revista (RE)DEFINIÇÕES DAS FRONTEIRAS, vol. 2, no. 6, pp. 16–43, jan. 2024.

    \item P. M. Fearnside and R. A. Silva, “Surpresas Climáticas: a Amazônia e as Lições da Enchente Catastrófica no Rio Grande do Sul,”  3 jul. 2024. [Online]. Available: \url{https://amazoniareal.com.br/licoes-da-enchente-catastrofica-no-rio-grande-do-sul/}
    
    \item G1, “Israel x Irã: tudo o que se sabe até o momento sobre o conflito,”  G1, 18 jun. 2025. [Online]. Available: \url{https://g1.globo.com/mundo/noticia/2025/06/18/israel-x-ira-tudo-o-que-se-sabe-ate-o-momento-sobre-o-conflito.ghtml}

    \item G1, “Israel realiza ataque aéreo contra Irã,”  G1, 12 jun. 2025. [Online]. Available: \url{https://g1.globo.com/mundo/noticia/2025/06/12/israel-realiza-aereo-contra-ira.ghtml}

    \item BBC News Brasil,  “EUA atacam instalações nucleares de Teerã,”  jun. 2025. [Online]. Available: \url{https://www.bbc.com/portuguese/articles/c3r9qgjwevdo}

    \item BBC News Brasil,  “Irã ataca bases militares dos EUA em retaliação,”  jun. 2025. [Online]. Available: \url{https://www.bbc.com/portuguese/articles/c0q8wwdldgpo}
\end{itemize}